Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-15 manuscript.tex

\title{Hurricane Evacuation Strategies for the State of Mississippi}
\author{A submission for the 2015 Cornell Mathematical Contest in Modeling \\ Prepared by Paul Chesnais, Antoine Pourchet and Ryan Vogan}
\date{November 16, 2015}

@@

\section{Abstract}
\label{sec:abstract}

\section{Executive Summary}
\label{sec:executive_summary}

% Antoine's stuff and thing
\section{Deterministic Model}
\label{sec:deterministic_model}

% Paul's stuff and things
\section{Stochastic Model}
\label{sec:stochastic_model}

\begin{thebibliography}{9}
  \bibitem{pmc}
    \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
  \bibitem{ms_highways}
    \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
\end{thebibliography}

>>>>

\title{Hurricane Evacuation Strategies for the State of Mississippi}
\author{Paul Chesnais (pmc85), Antoine Pourchet (app63), and Ryan Vogan (rcv39)\\2015 Cornell Mathematical Contest in Modeling\\November 16, 2015}
\date{}

@@

\section{Executive Summary}
\label{sec:summary}

\section{Introduction}
\label{sec:introduction}

\section{Model Assumptions}
\label{sec:assumptions}

\section{Statical Analysis of Historical Hurricane Data}
\label{sec:hurricanes}

\section{Markov Process Analysis of Strictly Northern Evacuations}
\label{sec:markov}
  \subsection{Model Description}
  \subsection{Parameter Values and Justification}
  \subsection{Results}
  \subsection{Strengths and Weaknesses}

\section{Maximum Flow Analysis of Strictly Northern Evacuations}
\label{sec:maxflow}
  \subsection{Model Description}
  \subsection{Parameter Values and Justification}
  \subsection{Results}
  \subsection{Strengths and Weaknesses}

\section{Stochastic Model of Landfall-Avodiant Evacuations}
\label{sec:stochastic}
  \subsection{Model Description}
  \subsection{Parameter Values and Justification}
  \subsection{Results}
  \subsection{Strengths and Weaknesses}

\section{Conclusions}
\label{sec:conclusions}

\section{Future Work}
\label{sec:future}

\section{Individual Contributions}
\label{sec:contributions}
  \begin{thebibliography}{9}
    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
    \bibitem{ms_highways}
      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
  \end{thebibliography}
